% $Author: $ $Date: $
% $Header: $ $Name:  $
% $Revision: $
%

\documentclass[a4paper,11pt]{letter}
\usepackage{latexsym,graphicx,multicol}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
% \usepackage{wrapfig,framed,longtable,tabularx,ltxtable}
\pagestyle{empty}
\signature{Simon ELBAZ}
\address{8, rue Belgrand\\ 92300 Levallois-Perret \\Mob.: +33 6 14 99 02 78\\}
\begin{document}

\begin{letter}{YouTube, Google\\ \bigskip Subject: Software Engineer in Test at YouTube, Google}
\opening{Dear Sir or Madam:}

I send you my candidacy for the position of Software Engineer in Test at YouTube.

This decision is motivated by the desire of staying near technical fields and to exploit my software programming experience in the world of IT.

As described in the job, test activity is an important facet of software industry. Particularly when it comes to content reachable by a large public: bugs are rapidly visible.

Being aware of this constraint, I would like to bring the experience acquired in Capgemini methodology (software life cycle) and during a long programmer experience at server levels or client levels.

I have been learning and using many open source softwares (Linux OS, Zope, libpqxx) during the different projects I have worked in. Those tools intensively use test automation and those test habits - from unit tests to complex scenarii - can be used in many programming contexts.

This may be a source of inspiration since open source community face the following challenge: complex software has to be tested with few human resources. Automation is the key word.

In a labor market particularly tense, I am fully motivated and willing to invest all my efforts working at YouTube. Without failing to mention that team spirit is essential to speed up comprehension and test of the delivered soft.

I remain at your disposal for further information.

\closing{Sincerely,}

\end{letter}
\end{document}
